\subsection{Team organisation and roles}

\subsubsection{Team name}
The team name {\textbf{CDOSR}} stands for Coderdojo Oradea Space Robotics, a group focused on space and robotics technologies, originating from CoderDojo Oradea. 

CoderDojo Oradea is a community-based programming club in Oradea, Romania, part of the global CoderDojo network offering free coding sessions for youth aged 7-17. Its goal is to inspire young people to learn coding and explore technology in a fun, supportive environment.

CDOSR is a specialized division within CoderDojo Oradea, focusing on space robotics. It brings together young enthusiasts passionate about space exploration and robotics, providing a platform for learning, collaboration, and innovation in space-related challenges.


\subsubsection{Team composition}

The CoderDojo Oradea Space Robotics team, comprising a leader and five members aged 15-18 from various high schools in Oradea, emphasizes open communication for effective collaboration. Each member has primary and secondary roles, promoting learning within the team.
\vspace{1cm}
\begin{itemize}
    %\input{section_1/team_members/Daniel_Erzse}
    \input{section_1/team_members/Andrei_Tigan}
    \input{section_1/team_members/David_Chereches}
    \input{section_1/team_members/Daria_Fologea}
    \input{section_1/team_members/Alin_Lupau}
    \input{section_1/team_members/Andrei_Costea}
    \input{section_1/team_members/Mark_Trefi}
\end{itemize}

\subsubsection{Team's Activity:} 

The team has developed a 6-point action plan to ensure effective progression in the CanSat design and development process, including:
\begin{enumerate}[topsep=3pt]
    \item Efficiently collaborate on the project by leveraging the skills and expertise of each team member, assigning clear roles and responsibilities aligned with their interests and abilities. We must ensure each team member has a clear understanding of their role and responsibility in the project. This also includes creating a team environment that values input and feedback from all members.

    \item Establish a clear plan and timeline for the design, development, and testing phases of the CanSat. Developing a detailed plan outlining specific milestones, deadlines, and deliverables for each phase of the project is vital.

    \item Regularly communicate and meet to discuss progress, challenges, and potential solutions:
    \begin{itemize}[leftmargin=0.25cm,itemindent=0.5cm, noitemsep, topsep=2pt, label=\textbullet]
        \item Schedule regular team meetings to discuss progress and challenges.
        \item Provide updates on individual tasks and responsibilities to ensure the team is working efficiently and effectively.
        \item Encourage open communication and idea-sharing to facilitate collaboration and problem-solving.
    \end{itemize}
    \item Leverage a multitude of resources, particularly those available online, to bolster the team's advancement and growth:
    \begin{itemize}[leftmargin=0.25cm,itemindent=0.5cm, noitemsep, topsep=2pt, label=\textbullet]
        \item Actively seek out and employ a variety of online resources and tools that aid in the design and development stages of the project.
        \item Keep up to date with relevant news, updates, and industry trends to enhance the team's knowledge and expertise.
    \end{itemize}
    \item Continuously test and evaluate the CanSat's design to ensure it meets competition requirements and performs as expected:
    \begin{itemize}[leftmargin=0.25cm,itemindent=0.5cm, noitemsep, topsep=2pt, label=\textbullet]
        \item Develop a testing plan to ensure the CanSat design meets competition requirements and functions as expected.
        \item Regularly evaluate the design to identify areas for improvement and potential issues.
        \item Continuously iterate and improve the design based on feedback and testing results.
    \end{itemize}
    \item Seek feedback and input from mentors and advisors to enhance the design and development process:
    \begin{itemize}[leftmargin=0.25cm,itemindent=0.5cm, noitemsep, topsep=2pt, label=\textbullet]
        \item Regularly seek feedback and input from mentors and advisors to enhance the design and development process.
        \item Utilize feedback and input to improve the design and development process and enhance the team's knowledge and expertise.
    \end{itemize}
\end{enumerate}
