\section{Mechanical stress testing}\label{A33333}


\begin{itemize}[labelwidth=0cm, leftmargin=0cm, itemindent=0.7cm, noitemsep, topsep=0pt, label={}]
\item \textbf{Drop resistance test}:
\begin{itemize}[labelwidth=2cm, leftmargin=1.9cm, label=\ding{109}, noitemsep, topsep=2pt]
\item[\faTasks] \textbf{Task}: Conduct a crash test to ensure the payload components can withstand the impact of a fall.
\item[\faFlask] \textbf{Method}: Prototypes will be dropped from a tower or drone to achieve the required descent speed. A fall test without a parachute will also be performed. Optionally, a 3-axis accelerometer will be added to record any G-force during the test.
\item[{\faHourglass[3]}] \textbf{Estimated testing time duration}: Estimated to be a few hours.
\item[{\faCheckSquare}] \textbf{Acceptance criteria}: All components should remain intact, and the electronics should continue to work continuously.
\end{itemize}
\item \textbf{Long-term G-force tests}:
\begin{itemize}[labelwidth=2cm, leftmargin=1.9cm, label=\ding{109}, noitemsep, topsep=2pt]
\item[\faTasks] \textbf{Task}: Simulate the G-forces that may occur during rocket transport to test the CanSat components' endurance.
\item[\faFlask] \textbf{Method}: The payload model will be placed on a carousel or string and rapidly rotated to generate the required overload due to the centrifugal force.
\item[{\faHourglass[3]}] \textbf{Estimated testing time duration}: The test will last for several hours.
\item[{\faCheckSquare}] \textbf{Acceptance criteria}: All components should remain intact, and the electronics should continue to work continuously throughout the test period.
\end{itemize}
\end{itemize}