\section{Sensor testing}\label{A22}

\begin{itemize}[labelwidth=0cm, leftmargin=0cm, itemindent=0.7cm, noitemsep, topsep=0pt, label={}]
\item \textbf{Pressure sensor test}:
\begin{itemize}[labelwidth=2cm, leftmargin=1.9cm, label=\ding{109}, noitemsep, topsep=2pt]
\item[\faTasks] \textbf{Task}: Expose the used sensor to a pressure change and compare the results with a reference device.
\item[\faFlask] \textbf{Method}: Place the target and reference sensors in a sealed container with a known volume of air and measure the pressure change with a manometer or a barometer. The pressure can be changed by altering the volume of the container or by using a hand pump.
\item[{\faHourglass[3]}] \textbf{Estimated testing time duration}: 1-2 hours
\item[{\faCheckSquare}] \textbf{Acceptance criteria}: The test will be considered positive when both sensors show the same pressure without measuring errors.
\end{itemize}
\item \textbf{Temperature sensor test}:
\begin{itemize}[labelwidth=2cm, leftmargin=1.9cm, label=\ding{109}, noitemsep, topsep=2pt]
\item[\faTasks] \textbf{Task}:  Check whether the target device and the reference device show the same temperature within 24 hours 
\item[\faFlask] \textbf{Method}: Place both the target device and the reference device in the same location and monitor their temperature readings at regular intervals for 24 hours
\item[{\faHourglass[3]}] \textbf{Estimated testing time duration}:  24 hours
\item[{\faCheckSquare}] \textbf{Acceptance criteria}: The test will be considered positive when both sensors show the same temperature without significant deviation.
\end{itemize}
\item \textbf{Humidity sensor test}:
\begin{itemize}[labelwidth=2cm, leftmargin=1.9cm, label=\ding{109}, noitemsep, topsep=2pt]
\item[\faTasks] \textbf{Task}:  Place the target sensor and the reference device in a humidity chamber where the humidity will be increased or decreased to a specific level, and the readings will be compared.
\item[\faFlask] \textbf{Method}: The target sensor and the reference device will be placed in a humidity chamber where the humidity level will be gradually increased or decreased to a specific level. The readings from both sensors will be recorded and compared.
\item[{\faHourglass[3]}] \textbf{Estimated testing time duration}:  6 hours
\item[{\faCheckSquare}] \textbf{Acceptance criteria}: The test will be considered positive when both sensors show the same humidity level without significant deviation.
\end{itemize}
\item \textbf{UV sensor test}:
\begin{itemize}[labelwidth=2cm, leftmargin=1.9cm, label=\ding{109}, noitemsep, topsep=2pt]
\item[\faTasks] \textbf{Task}:  Expose the target sensor and the reference device to UV radiation from a UV light source and compare the readings.
\item[\faFlask] \textbf{Method}: The target sensor and the reference device will be exposed to UV radiation from a UV light source for a specific duration, and the readings will be recorded and compared.
\item[{\faHourglass[3]}] \textbf{Estimated testing time duration}:  1 hour
\item[{\faCheckSquare}] \textbf{Acceptance criteria}: The test will be considered positive when both sensors show the same UV index without significant deviation.
\end{itemize}
\item \textbf{GPS test}:
\begin{itemize}[labelwidth=2cm, leftmargin=1.9cm, label=\ding{109}, noitemsep, topsep=2pt]
\item[\faTasks] \textbf{Task}:  Test the accuracy of the GPS module by comparing the location obtained by the CanSat with the actual location.
\item[\faFlask] \textbf{Method}: The location data collected by the GPS module during this time will be recorded and compared to the actual location using a separate reference system. The reference system may be a ground-based GPS receiver or a separate device with accurate location data.
\item[{\faHourglass[3]}] \textbf{Estimated testing time duration}:  1 hour
\item[{\faCheckSquare}] \textbf{Acceptance criteria}: The test will be considered positive if the error margin is within an acceptable range.
\end{itemize}
\end{itemize}
