\subsection{Outreach Program}

Our outreach program has two primary objectives. The first is to promote the interrelated STEM disciplines, Science, Technology, Engineering, and Mathematics, and highlight their distinct but interconnected nature. These four fields are essential in shaping the future of technological advancements and scientific discoveries, and we aim to inspire the next generation to pursue careers in STEM-related fields.

The second objective of our outreach program is to popularize the space sector and space exploration. We aim to educate the public about the importance of space technologies and how they impact our daily lives. 
%Furthermore, we want to showcase the role of CanSats in space exploration and highlight the various stages involved in their development, from design to launch. 
Through our outreach efforts, we hope to inspire the public to take an interest in space exploration and encourage the pursuit of careers in the space industry.

The team has made a detailed plan for raising awareness of the CanSat project and getting people involved. Different actions are included in this outreach plan to get the word out about the project. These include:
\begin{multicols}{2}[\vspace{-0.5\baselineskip}]
        \begin{itemize}[leftmargin=1cm,itemindent=0.5cm,noitemsep, topsep=0pt, label=$\bullet$]
%\begin{itemize}[, noitemsep, topsep=0pt]
\item presentations
% \item workshops
\item demonstrations
\item social media
\item websites
\item community engagement
\item participation in science fairs or events.
\end{itemize}
\end{multicols}
\vspace*{-0.5\baselineskip}

In addition to outlining the different types of outreach activities that the team will undertake, it is essential to consider each activity's expected audience, message, medium, and outcome.

Different groups, like schools and community centers, will get presentations about the CanSat project and the technology it uses.The outcome of these activities will be to increase awareness and interest in the CanSat project and inspire the audience to pursue STEM-related fields.

Social media platforms such as Twitter, Instagram, and Facebook will be used to document the team's progress and share updates about the project with the public. A website will be developed to provide detailed information about the project, including updates on the progress, photos, videos, and data from the mission. The message will focus on providing regular updates about the project, including its progress, challenges, and successes. The outcome of these activities will be to increase engagement and interest in the CanSat project and to create a sense of community around it.

For science fairs or events, the target audience will be students, teachers, and members of the public interested in STEM education and space technology. The main point of the message will be to show them the CanSat project and how it can help people come up with new ideas and solve problems. 



% \begin{table}[ht]
% \centering
% \begin{tabular}{|>{\centering\arraybackslash}p{2.2cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}|}
% \hline
% Activities & Audience & Message & Medium & Outcome\\
% \hline
% Presentations and workshops & Schools, community groups, and other organizations interested in STEM education & 
% Importance of STEM fields, the relevance of CanSat technology, and the process of designing and building a CanSat& 
% PowerPoint presentations and interactive demonstrations using physical models or simulators & 
% Increase awareness and interest in the CanSat project and inspire the audience to pursue STEM-related fields\\
% Social media and websites & General public, including students, teachers, parents, and space enthusiasts & Providing regular updates about the CanSat project, including its progress, challenges, and successes &  Text, photos, and videos & Increase engagement and interest in the CanSat project and to create a sense of community around it\\
% Community engagement activities & Local communities, including students, teachers, parents, and members of the public & Importance of STEM fields and the potential of CanSat technology to inspire innovation and problem-solving & 
% Interactive discussions, Q\&A sessions, and hands-on demonstrations of CanSat models or simulators & 
% Foster a sense of community engagement and to increase interest and awareness of the CanSat project and STEM fields\\
% Science fairs or events & Students, teachers, and members of the public interested in STEM education and space technology &Showcasing the CanSat project and its potential to inspire innovation and problem-solving & Physical demonstrations of CanSat models or simulators and interactive discussions about the CanSat project & Increase awareness and interest in the CanSat project and to inspire the next generation of space enthusiasts and innovators\\
% \hline
% \end{tabular}
% \caption{Outreach activities.}
% \end{table}