Effective project planning is essential for the successful design and construction of our proposed mission. From the outset, our team established a series of milestones that must be achieved during the competition phases. Accomplishing these milestones requires specific tasks, such as acquiring financial resources, identifying the most suitable materials, selecting high-performance sensors, and sourcing electronic components. Therefore, through discussions and careful planning, we have established a comprehensive plan to ensure the success of our project.

Our timeline takes into account every aspect of the project, including report writing, design, construction, launch, and testing. We have carefully allocated the necessary time and resources to each stage of the project to ensure that we meet our deadlines and achieve our goals. Regular progress checks will be conducted to ensure that we stay on track and make any necessary adjustments to our plan.

In addition to our internal timeline, we have also taken into consideration external factors, such as competition deadlines and launch availability, to ensure that we meet all necessary requirements and complete the project within the given timeframe.

By following our comprehensive timeline and adhering to our milestones, we are confident that we will successfully design, build, launch, and test our CanSat project.

\subsection{Time schedule of the CanSat/Payload preparation}\label{time_schedule}
To obtain a comprehensive understanding of our project's timeline, please refer to the milestones in Appendix \ref{A33}. 

By achieving these milestones, we will ensure the success of our CanSat project and meet our project goals and deadlines.

