\subsection{Team organization and roles}

\subsubsection{Team name}
The team name {\textbf{CDOSR}} stands for Coderdojo Oradea Space Robotics, a group focused on space and robotics technologies, originating from CoderDojo Oradea. CDOSR is also a long-time participant in the CanSat competition, showcasing its expertise and passion for space-related projects.

CoderDojo Oradea is a community programming club in Oradea, Romania, part of the global CoderDojo network that offers free coding sessions for young people aged 7-17. Its goal is to inspire young people to learn programming and explore technology in a fun and supportive environment.

CDOSR represents a branch within CoderDojo Oradea, concentrating on space robotics. It brings together young enthusiasts passionate about space exploration and robotics, providing a platform for learning, collaboration, and innovation in space-related challenges.


\subsubsection{Team composition}

The CoderDojo Oradea Space Robotics team, comprising a leader and five members aged 16-17 of various high schools in Oradea, emphasizes open communication for effective collaboration. To foster a collaborative learning environment, each team member is assigned a primary role and two secondary roles. This structure ensures a balanced distribution of responsibilities while encouraging skill development across diverse areas. Below is the team role assignment matrix, which outlines the roles and responsibilities of each member:


\begin{table}[htb]
    \centering
    \arrayrulecolor{CDOSRPrimary}
        \begin{tabular}{>{\centering\arraybackslash}l|*{6}{c}}
        \hline
        \rowcolor{CDOSRPrimary}
        \textbf{\color{white!50}\footnotesize{Role / Person}} & \textbf{\color{white!50}\footnotesize{Alin}} & \textbf{\color{white!50}\footnotesize{David}} & \textbf{\color{white!50}\footnotesize{Mark}} & \textbf{\color{white!50}\footnotesize{\c{S}tefan}} & \textbf{\color{white!50}\footnotesize{Antonio}} & \textbf{\color{white!50}\footnotesize{Miruna}} \\
        \rowcolor{CDOSRPrimary}
        & \textbf{\color{white!50}\footnotesize{Lup\u{a}u}} & \textbf{\color{white!50}\footnotesize{Chereche\c{s}}} & \textbf{\color{white!50}\footnotesize{Trefi}} & \textbf{\color{white!50}\footnotesize{Mierea}} & \textbf{\color{white!50}\footnotesize{Laza}} & \textbf{\color{white!50}\footnotesize{Ursu}} \\
        \hline
        \footnotesize{Hardware Design} & & \color{CDOSRWarning!80}\faCheckSquare & & \color{CDOSRWarning!80}\faCheckSquare & \color{CDOSRPrimary}\faCheckSquare & \\
        \rowcolor{CDOSRSecondary!50}
        \footnotesize{Software Design} \& Programming & \color{CDOSRPrimary}\faCheckSquare & \color{CDOSRWarning!80}\faCheckSquare & & & \color{CDOSRWarning!80}\faCheckSquare & \\
        \footnotesize{Data Analysis} \& Interpretation & \color{CDOSRWarning!80}\faCheckSquare & & & \color{CDOSRWarning!80}\faCheckSquare & & \color{CDOSRPrimary}\faCheckSquare \\
        \rowcolor{CDOSRSecondary!50}
        \footnotesize{3D Modeling} & & & \color{CDOSRPrimary}\faCheckSquare & & \color{CDOSRWarning!80}\faCheckSquare & \color{CDOSRWarning!80}\faCheckSquare \\
        \footnotesize{Base Operator, Radio} & \color{CDOSRWarning!80}\faCheckSquare & \color{CDOSRPrimary}\faCheckSquare & \color{CDOSRWarning!80}\faCheckSquare & & & \\
        \rowcolor{CDOSRSecondary!50}
        \footnotesize{Social Networking} & & & \color{CDOSRWarning!80}\faCheckSquare & \color{CDOSRPrimary}\faCheckSquare & & \color{CDOSRWarning!80}\faCheckSquare \\
        \hline
        \end{tabular}
        \caption{\small{Team Role Assignment Matrix}}
    \end{table}

% \vspace{0.5cm}
\begin{itemize}[leftmargin=*]
    %\input{section_1/team_members/Daniel_Erzse}
    \input{section_1/team_members/Alin_Lupau}
    \input{section_1/team_members/David_Chereches}
    \input{section_1/team_members/Mark_Trefi}
    \input{section_1/team_members/Stefan_Mierea}
    \input{section_1/team_members/Antonio_Laza}
    \input{section_1/team_members/Miruna_Ursu}
\end{itemize}

\subsubsection{Team's activity} 

The team has developed a six-point action plan to ensure the successful design, development, and testing of the CanSat. This structured approach emphasizes collaboration, planning, and continuous improvement to meet competition requirements and achieve optimal performance. The plan includes the following key steps:
\begin{enumerate}[topsep=3pt]
    \item Effective Collaboration 
        \begin{itemize}[leftmargin=0.25cm,itemindent=0.5cm, noitemsep, topsep=1pt, label=\textbullet]
            \myitemtwo Leverage the unique skills and expertise of each team member by assigning clear roles and responsibilities aligned with their strengths and interests.
            \myitemtwo Ensure every member understands their tasks and contributions to the project.
            \myitemtwo Create a team environment that encourages open communication, values diverse perspectives, and promotes constructive feedback.
        \end{itemize}
    \item Establish a clear project plan and timeline 
        \begin{itemize}[leftmargin=0.25cm,itemindent=0.5cm, noitemsep, topsep=1pt, label=\textbullet]
            \myitemtwo Develop a detailed roadmap outlining specific milestones, deadlines, and deliverables for each phase of the project (design, development, and testing).
            \myitemtwo Allocate sufficient time for iterative improvements and unexpected challenges.
        \end{itemize}
    \item Maintain regular communication and progress updates
        \begin{itemize}[leftmargin=0.25cm,itemindent=0.5cm, noitemsep, topsep=1pt, label=\textbullet]
            \myitemtwo Schedule regular team meetings to discuss progress and challenges.
            \myitemtwo Provide updates on individual tasks and responsibilities to ensure that the team is working efficiently and effectively.
            \myitemtwo Encourage open communication and idea sharing to facilitate collaboration and problem solving.
        \end{itemize}
    \item Utilize diverse resources for continuous learning
        \begin{itemize}[leftmargin=0.25cm,itemindent=0.5cm, noitemsep, topsep=1pt, label=\textbullet]
            \myitemtwo Actively seek and employ online tools, tutorials, and resources to support the design and development process.
            \myitemtwo Stay informed about industry trends, technological advancements, and best practices to enhance the team’s knowledge and innovation.
        \end{itemize}
    \item Implement rigorous testing and evaluation
        \begin{itemize}[leftmargin=0.25cm,itemindent=0.5cm, noitemsep, topsep=1pt, label=\textbullet]
            \myitemtwo Develop a comprehensive testing plan to ensure the CanSat meets competition requirements and performs as intended.
            \myitemtwo Regularly evaluate the design to identify areas for improvement and address potential issues.
            \myitemtwo Iterate and refine the design based on testing results and feedback.
        \end{itemize}
    \item Seek mentorship and expert guidance
        \begin{itemize}[leftmargin=0.25cm,itemindent=0.5cm, noitemsep, topsep=1pt, label=\textbullet]
            \myitemtwo Regularly seek feedback and input from mentors and advisors to enhance the design and development process.
            \myitemtwo Utilize feedback and input to improve the design and development process and enhance the team's knowledge and expertise.
        \end{itemize}
\end{enumerate}
